### 2021-04-04 newvariant.tex
one more paragraph

>>>>

\fref{relspeed} also shows that relative speed depends on underlying epidemiological conditions. 
For example, even when there are no differences in the generation-interval distributions ($\Gv=\Gw$, in this case), the relative speed $\delta$ can range between 0.08--0.11 when $\kappa=0.2$ and 0.06--0.14 when $\kappa=0.5$.
Therefore, characterizing the spread of variants assuming constant relative speed (e.g., by fitting a standard logistic equation) without considering how epidemiological conditions change over time should be avoided.
